FLM for growth as function of SPEI

### 2021-01-20 analysis/paper/vital rate models.Rmd
Changed growth plot to ∆size.  Worked on axis labels and exporting covariate plots. Closes #21

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, paged.print=FALSE)
library(tidyverse)
library(here)
library(mgcv)
library(dlnm)
library(bbmle)
library(lubridate)
library(glue)
library(patchwork)
library(sf)
library(tsibble)
library(broom)
library(gratia)

@@

```{r}
cl <- parallel::makeForkCluster()
```

@@

```{r}
range(demog_post_cf$log_size)

newdata <- 
  tibble(log_size = seq(0, 7.8, length.out = 100),
         plot = "newplot",
         year_fac = "newyear", 
         spei_history = mean(demog_post_cf$spei_history),
         L = demog_post_cf$L[1:100, ])

out <- augment(g_post_cf, newdata = newdata, se_fit = TRUE)

covar_growth_cf <-
  ggplot(out, aes(x = exp(log_size), y = exp(.fitted))) + 
  geom_point(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.1) +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit * 1.96), ymax = exp(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw() +
  labs(x = "size in year t (shoots * height)", y = "size in year t+1 (shoots * height)")
covar_growth_cf
```
```{r}
range(demog_post_1ha$log_size)

newdata <- 
  tibble(log_size = seq(0, 7.6, length.out = 100),
         plot = "newplot",
         year_fac = "newyear",
         spei_history = mean(demog_post_1ha$spei_history),
         L = demog_post_cf$L[1:100, ])
out <- augment(g_post_1ha, newdata = newdata, se_fit = TRUE)

covar_growth_1ha <-
  ggplot(out, aes(x = exp(log_size), y = exp(.fitted))) + 
  geom_point(data = demog_post_1ha, aes(x = size, y = size_next), alpha = 0.1) +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit * 1.96), ymax = exp(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_1ha, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw() +
  labs(x = "size in year t (shoots * height)", y = "size in year t+1 (shoots * height)")
covar_growth_1ha
```

@@

```{r}
# use mean size plant across both habitats so plots are comparable
ref_data <-
  demog_post %>%
  dplyr::summarize(log_size = log(mean(size, na.rm = TRUE)),  #log of mean size, not mean of log_size
                   year_fac = "newyear",
                   plot = "newlevel")
# exp(1.032814) # 2.8 shoots
mean_size <- round(exp(ref_data$log_size), 1)
```

@@

@@

```{r}
shoot_lim <- c(min(pred_g_post_1ha$fitted, pred_g_post_cf$fitted),
               max(pred_g_post_1ha$fitted, pred_g_post_cf$fitted))
```

@@

TODO: make color be ∆size (i.e. fitted - mean size from ref_data)

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("size(t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_growth_cf
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_growth_1ha
```

@@

```{r}
p_growth_cf_slice <-
  pred_g_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "Continuous Forest", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_cf_slice
```

```{r}
p_growth_1ha_slice <-
  pred_g_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "1-ha Fragments", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_1ha_slice
```

@@

```{r}
#TODO: replace with ridge plot
plotdf <-
  pred_g_post_cf %>% 
  mutate(lag = round(lag)) %>% 
  group_by(x, lag) %>% 
  summarize(across(everything(),  mean))

foo <- function(x) {
  x <- as.numeric(x)
  mon <- month(ymd("2020-2-01") - months(x), label = TRUE)
  l <- glue("lag={x} ({mon})")
  return(l)
}

p_growth_cf_months <-
  plotdf %>% 
  ggplot(aes(x = x, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("SPEI3") +
  scale_y_continuous("shoots (t+1)") +
  facet_wrap(~lag, labeller = as_labeller(foo)) +
  theme_bw()
p_growth_cf_months
```

@@

```{r}
range(demog_post_cf$log_size)
newdata <- 
  tibble(log_size = seq(0, 7.8, length.out = 100),
         plot = "newplot",
         year_fac = "newyear",
         spei_history = mean(demog_post_cf$spei_history),
         L = demog_post_cf$L[1:100, ])
out <- augment(s_post_cf, newdata = newdata, se_fit = TRUE)

covar_s_cf <-
  ggplot(out, aes(x = log_size, y = plogis(.fitted))) + 
  # geom_point(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.1) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw()
covar_s_cf
```

@@

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_surv_cf
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_surv_1ha
```

@@

```{r}
x <- demog_post_cf$flwr
sum(x, na.rm = TRUE) / length(x)
```

@@

```{r}
appraise(f_post_cf)
```
these residuals are troubling

@@

@@

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
```

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
```
very similar to growth

@@

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth of average sized plant (~2.8 shoots)") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_growth_spei
ggsave(here("analysis", "figures", "growth_spei.png"), p_growth_spei, height = 7, width = 14)
```

It looks like drought in September/October is bad for growth.

Reminder that these are still fit with two different models and might not be entirely comparable.  Different penalties to the smooths make these hard to compare as well.

Here's a slice through SPEI = -1.5 (severe drought)

```{r}
(p_growth_cf_slice + theme(axis.text.x = element_blank())) /
  p_growth_1ha_slice +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5) on average sized plant (~2.8 shoots)")
ggsave(here("analysis", "figures", "growth slice.png"))
```

Again, you can see that drought immediately preceding the census (Jan of that year) and in the previous October are bad for growth, but dry Decembers and Septembers are good for growth.

@@

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk & labs(caption="")
p_surv_spei
ggsave(here("analysis", "figures", "surv_spei.png"), p_surv_spei, width = 14, height = 7)
```

The surface for 1-ha fragments is basically flat except for a slight *negative* effect of recent wet weather on survival.  In continuous forest, wet conditions or very dry conditions in the previous August–October have a positive effect on survival.

Here's a slice through SPEI = -1.5 (severe drought)

```{r}
((p_surv_cf_slice + theme(axis.text.x = element_blank())) / p_surv_1ha_slice) +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5)")
ggsave(here("analysis", "figures", "survival slice.png"))
```
Pretty flat.

@@

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_flowered_spei
ggsave(here("analysis", "figures", "flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```

The surface for continuous forest is perfectly flat (did I do something wrong with the color scale?) and for 1-ha fragments there is a strange (anomalous?) negative effect of high SPEI (wet conditions) in the summer 2 years ago.

Here's a slice through SPEI = -1.5 (severe drought)

```{r}
((p_flowered_cf_slice + theme(axis.text.x = element_blank())) / p_flowered_1ha_slice) +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5)")
ggsave(here("analysis", "figures", "flowering slice.png"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, paged.print=FALSE)
library(tidyverse)
library(here)
library(mgcv)
library(dlnm)
library(bbmle)
library(lubridate)
library(glue)
library(patchwork)
library(sf)
library(tsibble)
library(broom)
library(gratia)
library(latex2exp)

@@

```{r}
library(parallel)
ncores <- detectCores()
cl <- makeForkCluster(ncores - 2)
```

@@

```{r}
sr <- range(demog_post_cf$log_size)

newdata_covar_cf <- 
  tibble(log_size = seq(sr[1], sr[2], length.out = 100),
         plot = "newplot",
         year_fac = "newyear", 
         spei_history = mean(demog_post_cf$spei_history),
         L = demog_post_cf$L[1:100, ])

out <- augment(g_post_cf, newdata = newdata_covar_cf, se_fit = TRUE)

covar_growth_cf <-
  ggplot(out, aes(x = exp(log_size), y = exp(.fitted))) + 
  geom_point(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.1) +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit * 1.96), ymax = exp(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw() +
  labs(x = TeX("size_t_"), y = TeX("size_{t+1}_"))
covar_growth_cf
ggsave(here("analysis", "figures", "growth_cf_size.png"), covar_growth_cf)
```
```{r}
sr <- range(demog_post_1ha$log_size)
newdata_covar_1ha <- 
  tibble(log_size = seq(sr[1], sr[2], length.out = 100),
         plot = "newplot",
         year_fac = "newyear",
         spei_history = mean(demog_post_1ha$spei_history),
         L = demog_post_cf$L[1:100, ])

out <- augment(g_post_1ha, newdata = newdata_covar_1ha, se_fit = TRUE)

covar_growth_1ha <-
  ggplot(out, aes(x = exp(log_size), y = exp(.fitted))) + 
  geom_point(data = demog_post_1ha, aes(x = size, y = size_next), alpha = 0.1) +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit * 1.96), ymax = exp(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_1ha, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw() +
  labs(x = TeX("size_t_"), y = TeX("size_{t+1}_"))

covar_growth_1ha
ggsave(here("analysis", "figures", "growth_1ha_size.png"), covar_growth_1ha)
```

@@

```{r}
# use mean size plant across both habitats so plots are comparable
ref_data <-
  demog_post %>%
  dplyr::summarize(log_size = log(mean(size, na.rm = TRUE)),  #log of mean size, not mean of log_size
                   year_fac = "newyear",
                   plot = "newlevel")

mean_size <- exp(ref_data$log_size)
```

@@

Calculate growth as change from year t to year t+1

```{r}
mean_size # size in year t for fitted values

pred_g_post_cf <- 
  pred_g_post_cf %>% 
  mutate(e_fitted = exp(fitted),
         d_fitted = e_fitted - mean_size)

pred_g_post_1ha <-
  pred_g_post_1ha %>% 
  mutate(e_fitted = exp(fitted),
         d_fitted = e_fitted - mean_size)
```

@@

```{r}
shoot_lim <- c(min(pred_g_post_1ha$d_fitted, pred_g_post_cf$d_fitted),
               max(pred_g_post_1ha$d_fitted, pred_g_post_cf$d_fitted))
```

@@

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = d_fitted, fill = d_fitted)) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c(TeX("$\\Delta$ size"), option = "A", limits = shoot_lim) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_growth_cf
ggsave(here("analysis", "figures", "growth_cf_spei.png"), p_growth_cf)
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = d_fitted, fill = d_fitted)) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c(TeX("$\\Delta$ size"), option = "A", limits = shoot_lim) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_growth_1ha
ggsave(here("analysis", "figures", "growth_1ha_spei.png"), p_growth_1ha)
```

@@

```{r}
# p_growth_cf_slice <-
#   pred_g_post_cf %>% 
#   filter(nearest(x, -1.50)) %>% 
#   ggplot(aes(x = lag, y = exp(fitted))) +
#   geom_ribbon(aes(
#     ymin = exp(fitted - se.fit * 1.96),
#     ymax = exp(fitted + se.fit * 1.96)
#   ), alpha = 0.3)+
#   geom_line() +
#   scale_x_continuous("lag(months)", breaks = 0:36) +
#   labs(title = "Continuous Forest", y = "shoots (t+1)") +
#   theme_linedraw()
# p_growth_cf_slice
```

```{r}
# p_growth_1ha_slice <-
#   pred_g_post_1ha %>% 
#   filter(nearest(x, -1.5)) %>% 
#   ggplot(aes(x = lag, y = exp(fitted))) +
#   geom_ribbon(aes(
#     ymin = exp(fitted - se.fit * 1.96),
#     ymax = exp(fitted + se.fit * 1.96)
#   ), alpha = 0.3)+
#   geom_line() +
#   scale_x_continuous("lag(months)", breaks = 0:36) +
#   labs(title = "1-ha Fragments", y = "shoots (t+1)") +
#   theme_linedraw()
# p_growth_1ha_slice
```

@@

```{r}
# #TODO: replace with ridge plot
# plotdf <-
#   pred_g_post_cf %>% 
#   mutate(lag = round(lag)) %>% 
#   group_by(x, lag) %>% 
#   summarize(across(everything(),  mean))
# 
# foo <- function(x) {
#   x <- as.numeric(x)
#   mon <- month(ymd("2020-2-01") - months(x), label = TRUE)
#   l <- glue("lag={x} ({mon})")
#   return(l)
# }
# 
# p_growth_cf_months <-
#   plotdf %>% 
#   ggplot(aes(x = x, y = exp(fitted))) +
#   geom_ribbon(aes(
#     ymin = exp(fitted - se.fit * 1.96),
#     ymax = exp(fitted + se.fit * 1.96)
#   ), alpha = 0.3)+
#   geom_line() +
#   scale_x_continuous("SPEI3") +
#   scale_y_continuous("shoots (t+1)") +
#   facet_wrap(~lag, labeller = as_labeller(foo)) +
#   theme_bw()
# p_growth_cf_months
```

@@

```{r}
out <- augment(s_post_cf, newdata = newdata_covar_cf, se_fit = TRUE)

covar_s_cf <-
  ggplot(out, aes(x = exp(log_size), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = surv), data = demog_post_cf) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(survival)") +
  theme_linedraw()

covar_s_cf
ggsave(here("analysis", "figures", "surv_cf_size.png"), covar_s_cf)
```

Uh...There might be something wrong with how I've determined survival.  I should revisit this.

```{r}
out <- augment(s_post_1ha, newdata = newdata_covar_1ha, se_fit = TRUE)

covar_s_1ha <-
  ggplot(out, aes(x = exp(log_size), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = surv), data = demog_post_1ha) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(survival)") +
  theme_linedraw()

covar_s_1ha
ggsave(here("analysis", "figures", "surv_1ha_size.png"), covar_s_1ha)
```

@@

```{r}
#mean survival
x <- demog_post$surv
sum(x, na.rm = TRUE) / length(x)
```

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_surv_cf
ggsave(here("analysis", "figures", "surv_cf_spei.png"), p_surv_cf)
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_surv_1ha
ggsave(here("analysis", "figures", "surv_1ha_spei.png"), p_surv_1ha)
```

@@

```{r}
x <- demog_post$flwr
sum(x, na.rm = TRUE) / length(x)
```

@@

Doesn't converge with random effect of year

```{r}
appraise(f_post_cf)
# concurvity(f_post_cf, full = FALSE)
```
these residuals are troubling

@@

## Covariate plots
Effect of size with all else held average.

```{r}
out <- augment(f_post_cf, newdata = newdata_covar_cf, se_fit = TRUE)

covar_f_cf <-
  ggplot(out, aes(x = exp(log_size), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = flwr), data = demog_post_cf) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(flowering)") +
  theme_linedraw()

covar_f_cf
ggsave(here("analysis", "figures", "flwr_cf_size.png"), covar_f_cf)
```

```{r}
out <- augment(f_post_1ha, newdata = newdata_covar_1ha, se_fit = TRUE)

covar_f_1ha <-
  ggplot(out, aes(x = exp(log_size), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = flwr), data = demog_post_1ha) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(flowering)") +
  theme_linedraw()

covar_f_1ha
ggsave(here("analysis", "figures", "flwr_1ha_size.png"), covar_f_1ha)
```
## Get plot data

@@

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
ggsave(here("analysis", "figures", "flwr_cf_spei.png"), p_flowered_cf)
```

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
ggsave(here("analysis", "figures", "flwr_1ha_spei.png"), p_flowered_1ha)
```
very similar to growth

@@

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_growth_spei
# ggsave(here("analysis", "figures", "growth_spei.png"), p_growth_spei, height = 7, width = 14)
```

@@

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk & labs(caption="")
p_surv_spei
# ggsave(here("analysis", "figures", "surv_spei.png"), p_surv_spei, width = 14, height = 7)
```

@@

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_flowered_spei
# ggsave(here("analysis", "figures", "flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```
